%* indica para nao adicionar numeracao ao titulo
\chapter*{Acknowledgments}

First of all, I would like to thank God for giving me health and concentration during the COVID19 crises in Europe and for not allowing anything bad to happen with me.

Also, I leave my immense gratitude for the University of Brasilia for the acquired knowledge along these years.


I am eternally thankful to my family Alessandra Justino, Flávio Praciano, Lenita Justino, and Victor Hugo, whom I can count and trust unconditionally.

An invaluable character is my master tutor Prof. Dr.-Ing. Joao Paulo C. L da Costa, who directed me to the new field of autonomous vehicles, and for always motivate me to do my best.

I would like to demonstrate my gratitude for my advisor Lothar Weichenberger for trust in my work and always support me and a special thanks for the company Elektronische Fahrwerksystem GmbH for financial and structural support. Another very essential characters in my thesis are Lukac Branimir, Tobias Behn, and Andreas Schustek without their valuable support it would not possible to do much of my work.

Along this road, I had some problems with german bureaucracy, my sincere thanks for Lukas Bös for his unbelievable capacity to solve problems and his communication skills, also I need to thank Sara Martin and Robin Käsmayr for their support and also students who attended our Stammtisch. And Vanessa Voll for all the help provided.

I would like to thanks the lunch clubs of Latino brothers composed by Javier Rivas, Arnaldo Arancíbia, Gabriel Pinheiro, João Paulo, and me for the good conversations and for supporting me to improve my Spanish while I was living in Germany.

My time in Germany was excellent due to the great hospitality of my host family, my thankful to Johanna Hirschmann and Herbert Hirschmann for made it easy everything. 

Additionally, his unconditional helpfulness and psychological support were simply
crucial, my friends were very important, in special my flatmate Gabriel Pinheiro, Lucas Maciel, Yan Trindade, Fábio Mendonça, Daniel Alves, Francisco Lopes, Robson de Albuquerque, and Rafael Timoteo. 

I also express my sincere gratitude for the professors from the University of Brasilia in special for Prof.Dr. Rafael Timoteo de Sousa Junior for his invaluable support and his guidance along with my career. And for prof. Dr. Edna Canedo, prof. Dr. Georges Amvame for partnership in some papers publications.

My sincere gratitude for the Institutional Security Office of the Presidency of the Republic of Brazil (Grant 002/2017) and to FAPDF (Projetos UIoT 0193.001366/2016) whose I have a scholarship and supported me to pay the conference fees. 